Supplement

### 2023-10-16 paper/supplement.Rmd
rerun models; add closeness and pre-reg stuff to ms

header-includes:
 - \usepackage{tikz}
 - \usetikzlibrary{positioning,arrows.meta, quotes, shapes}
---

@@

@@

```{r}
knitr::kable(predint, col.names=NULL, align='rrlrlrlrl',position="!h", caption="Coefficients and 95\\% CrI from linear models predictiong the p-original value between the original and replicaiton effects. All pairs indicates that all pairs with calculable prediction intervals were used, regardless of whether they had full statistical information; Full stats indicates that only data with full statistical information was used. Sensitivity indicates that it was a sensitivity test.", booktabs=T, linesep="") |> kable_styling() |>  
  add_header_above(c(" " = 1, "N=136" = 2, "N=112" = 2, "N=100" = 2, "N=82"=2)) |> 
 add_header_above(c(" " = 1, " " = 2, " " = 2, "Sensitivity" = 2, "Sensitivity"=2)) |> add_header_above(c(" " = 1, "All pairs" = 2, "Full stats" = 2, "All pairs" = 2, "Full stats"=2))

@@

# Sub sample of Psych Science papers

>>>>

header-includes:
 - \usepackage{tikz}
 - \usetikzlibrary{positioning,arrows.meta, quotes, shapes}
 - \usepackage{placeins}
---

@@

\FloatBarrier

@@

```{r}
knitr::kable(porig, col.names=NULL, align='rrlrlrlrl',position="!h", caption="Coefficients and 95\\% CrI from linear models predictiong the p-original value between the original and replicaiton effects. All pairs indicates that all pairs with calculable prediction intervals were used, regardless of whether they had full statistical information; Full stats indicates that only data with full statistical information was used. Sensitivity indicates that it was a sensitivity test.", booktabs=T, linesep="") |> kable_styling() |>  
  add_header_above(c(" " = 1, "N=136" = 2, "N=112" = 2, "N=100" = 2, "N=82"=2)) |> 
 add_header_above(c(" " = 1, " " = 2, " " = 2, "Sensitivity" = 2, "Sensitivity"=2)) |> add_header_above(c(" " = 1, "All pairs" = 2, "Full stats" = 2, "All pairs" = 2, "Full stats"=2))

@@

<!-- # Sub sample of Psych Science papers
